\LARGE Tailoring Differentially Private Bayesian Inference to Distance Between Distributions

### 2018-10-11 poster/main.tex
update the poster

\setbeamercolor{background canvas}{bg=white!20}

\usepackage[english]{babel} % English language/hyphenation

@@

\newcommand{\rightfoot}{mbun@cs.princeton.edu, gaboardi@buffalo.edu} % Right footer text

@@

\setbeamercolor{block title}{fg=black,bg=orange!70} % Change the block title color

>>>>

\setbeamercolor{background canvas}{bg=white!20}
% \setbeamercolor{block title}{fg=white,bg=blue!70}
% \setbeamercolor{block body}{fg=black,bg=blue!10}
\usepackage[english]{babel} % English language/hyphenation

@@

\newcommand{\rightfoot}{mbun@cs.princeton.edu, \{gianpiet,gaboardi,jliu223\}@buffalo.edu} % Right footer text

@@

\setbeamercolor{block title}{fg=black,bg=white!70} % Change the block title color
